Fictitious Play in Network Aggregative Games

### 2021-04-29 Documents/FP in NAGs/neurips_2020.tex
Included NeurIPS version

\documentclass{article}
\usepackage[margin=2cm]{geometry}
\usepackage{amsmath, amsfonts, amsthm}
\usepackage{xcolor}
\usepackage{enumerate}
\usepackage{graphicx}

@@

\title{Fictitious Play in Network Aggregative Games}
\author{AH, FB}

@@

	\section{Paper Structure}

	\begin{enumerate}
		\item Introduction: Explain the notion of a Network Aggregative Game, and Fictitious Play
		with literature on the state of the art. Assumptions made as well as summary of results
		\item Maybe? Relation with the model of Grammatico
		\item Preliminaries \begin{itemize}
			\item The Network Aggregative Game model
			\item Fictitious Play, as well as the CTFP property
		\end{itemize}
		\item Convergence of Fictitious Play \begin{itemize}
			\item Existence of the Nash Equilibrium
			\item Existence of a CTFP
			\item Convergence of CTFP to a fixed point
			\item Corrolary: when $w_{ii} = 0$ (i.e. the interaction graph is simple) CTFP converges
			to a NE
			\item Convergence of CTFP to the NA-CCE set
		\end{itemize}
		\item Numerical Experiments + Discussion \begin{itemize}
			\item Non-convergent examples
			\item Fictitious Play with Noise
		\end{itemize}
		\item Concluding Remarks
	\end{enumerate}

	\newpage
	\section{Introduction}

@@

	\subsection{Network Aggregative Games}
	\label{sec::NAG}

@@

@@

@@

	\section{Concluding remarks}
\end{document}

>>>>

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2020

% ready for submission
% \usepackage{neurips_2020}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2020}

% to compile a camera-ready version, add the [final] option, e.g.:
    % \usepackage[final]{neurips_2020}

% to avoid loading the natbib package, add option nonatbib:
     \usepackage[nonatbib]{neurips_2020}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{amsmath, amsfonts, amsthm}
\usepackage{xcolor}
\usepackage{enumerate}
\usepackage{graphicx}

@@

\title{Fictitious Play in Network Aggregative Games}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
 Aamal Hussain  \\
  Department of Computing\\
  Imperial College London\\
  South Kensington, London \\
  \texttt{aamal.hussain15@imperial.ac.uk} \\
  % examples of more authors
  \And
  Francesco Belardinelli
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

\section{Introduction}

@@

\section{Preliminaries}
\subsection{Network Aggregative Games}
\label{sec::NAG}

@@

\subsection{Convergence of CTFP}

@@

  \begin{figure}[t]
    \centering
    \includegraphics[width = \columnwidth]{Figures/Noise10Player.png}
    \caption{\label{fig::Noise10Player}}
  \end{figure}

  \begin{figure}[t]
    \centering
    \includegraphics[width = \columnwidth]{Figures/Noise20Player.png}
    \caption{\label{fig::Noise10Player}}
  \end{figure}

@@

\section{Concluding remarks}

\section*{Broader Impact}

Authors are required to include a statement of the broader impact of their work, including its ethical aspects and future societal consequences. 
Authors should discuss both positive and negative outcomes, if any. For instance, authors should discuss a) 
who may benefit from this research, b) who may be put at disadvantage from this research, c) what are the consequences of failure of the system, and d) whether the task/method leverages
biases in the data. If authors believe this is not applicable to them, authors can simply state this.

Use unnumbered first level headings for this section, which should go at the end of the paper. {\bf Note that this section does not count towards the eight pages of content that are allowed.}

\begin{ack}
Use unnumbered first level headings for the acknowledgments. All acknowledgments
go at the end of the paper before the list of references. Moreover, you are required to declare 
funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work). 
More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2020/PaperInformation/FundingDisclosure}.

Do {\bf not} include this section in the anonymized submission, only in the final paper. You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
\end{ack}

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
{\bf Note that the Reference section does not count towards the eight pages of content that are allowed.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.

\end{document}
